### 2015-03-06 paper_70_case-study.tex
updated sensitivity analysis and conclusion added latest PDF file

    \subsection{WITH HISTORICAL DATA}
        After the data has been collected, the raw data can be stored in the SDLC
        if desired.  Then scores for each of the 4 elements can be calculated.
        For this example, the value of $k$ will be 100 and the time
        frequency will be monthly.  Thus, scores will fall
        in the range $[-100,100]$.  Also, equal weighting is applied to 
        all elements and all Project IDs, Application IDs, and System IDs.
        \subsubsection{QUALITY}
            The first step to dealing with the quality data is a quick
            analysis of the data.  Table \ref{tab:quality_desc} provides
            some descriptive statistics for the quality data.  Testing hours
            were not capture but they are optional, so the analysis can 
            continue.

@@

        \subsubsection{AVAILABILITY}
            For the availability data,
            some descriptive statistics can be seen in 
            Table \ref{tab:availability_desc}.  The percent uptime
            was precalculated for this data so uptime, scheduled downtime,
            and unscheduled downtime are not needed.  Availability
            does not rely upon analysis of historical data since
            a known upper and lower bound exist, 1 and 0 respectively.

@@

        \subsubsection{SCHEDULE}
            Figure \ref{tab:schedule_desc} displays some descritive statistics
            for the schedule data.  Since the data is mostly dates, the 
            descriptive statistics are limited, so extra values were
            added to the table after removing 4 outliers.  The new values
            in the table are: Schedule Duration (Scheduled Finish - Scheduled Start),
            Difference (Actual Finish - Schedule Finish), and 
            $\Delta$ ($frac{\Delta}{\text{Schedule Duration}}$ ).

@@

        \subsubsection{REQUIREMENTS}
        \label{sec:case-req}
            The data for requirements is actually counts of story points
            instead of requirements.  That is because story points
            are a better choice for counting, since they are more
            uniform in size than raw requirements.  Also, the data
            contained 15 rows of data with a 0 for the number of
            scheduled requirements.  Those 15 rows were removed.
            Table \ref{tab:requirements_desc} shows some descriptive
            statistics for the remaining rows. A histogram for the
            data can be seen in Appendix \ref{app:requirements-hist}.

@@

        \subsubsection{OVERALL}
            Now it is time to combine the scores for the overall CRI.  Notice
            the schedule does not have scores for January 2014 or January 2015.
            Presumably, that is because the SDO within the large financial institution
            does not schedule projects to be completed in January. Much of the work
            would need to be completed over Christmas and New Year's Day, but many
            workers take personal time off of work during that time.  Thus some
            organizations will schedule appropriately.  CRI is well suited to
            handle this problem.  Just perform a weighted average over the
            applicable elements.  In this case study, the weights are all equal,
            so CRI is just a straight average.  Figure \ref{fig:cri-scores}
            displays the CRI scores as computed with the source code
            from Appendix \ref{src:overall}.  The scores are all above 0, so this
            financial institution is consistently performing better
            than expected.

@@

%%\subsection{WITHOUT HISTORICAL DATA}

%%An CRI calculation with default values for quality, schedule and requirements.

>>>>

    After the data has been collected, the raw data can be stored in the SDLC
    if desired.  Then scores for each of the 4 elements can be calculated.
    For this example, the value of $k$ will be 100 and the time
    frequency will be monthly.  Thus, scores will fall
    in the range $[-100,100]$.  Also, equal weighting is applied to 
    all elements and all Project IDs, Application IDs, and System IDs.

    \subsection{QUALITY}
        The first step to dealing with the quality data is a quick
        analysis of the data.  Table \ref{tab:quality_desc} provides
        some descriptive statistics for the quality data.  Testing hours
        were not capture but they are optional, so the analysis can 
        continue.

@@

    \subsection{AVAILABILITY}
        For the availability data,
        some descriptive statistics can be seen in 
        Table \ref{tab:availability_desc}.  The percent uptime
        was precalculated for this data so uptime, scheduled downtime,
        and unscheduled downtime are not needed.  Availability
        does not rely upon analysis of historical data since
        a known upper and lower bound exist, 1 and 0 respectively.

@@

    \subsection{SCHEDULE}
        Figure \ref{tab:schedule_desc} displays some descritive statistics
        for the schedule data.  Since the data is mostly dates, the 
        descriptive statistics are limited, so extra values were
        added to the table after removing 4 outliers.  The new values
        in the table are: Schedule Duration (Scheduled Finish - Scheduled Start),
        Difference (Actual Finish - Schedule Finish), and 
        $\Delta$ ($frac{\Delta}{\text{Schedule Duration}}$ ).

@@

    \subsection{REQUIREMENTS}
    \label{sec:case-req}
        The data for requirements is actually counts of story points
        instead of requirements.  That is because story points
        are a better choice for counting, since they are more
        uniform in size than raw requirements.  Also, the data
        contained 15 rows of data with a 0 for the number of
        scheduled requirements.  Those 15 rows were removed.
        Table \ref{tab:requirements_desc} shows some descriptive
        statistics for the remaining rows. A histogram for the
        data can be seen in Appendix \ref{app:requirements-hist}.

@@

    \subsection{OVERALL}
        Now it is time to combine the scores for the overall CRI.  Notice
        the schedule does not have scores for January 2014 or January 2015.
        Presumably, that is because the SDO within the large financial institution
        does not schedule projects to be completed in January. Much of the work
        would need to be completed over Christmas and New Year's Day, but many
        workers take personal time off of work during that time.  Thus some
        organizations will schedule appropriately.  CRI is well suited to
        handle this problem.  Just perform a weighted average over the
        applicable elements.  In this case study, the weights are all equal,
        so CRI is just a straight average.  Figure \ref{fig:cri-scores}
        displays the CRI scores as computed with the source code
        from Appendix \ref{src:overall}.  The scores are all above 0, so this
        financial institution is consistently performing better
        than expected.

@@

    \subsection{CORRELATION AND SENSITIVITY}
        Based upon the graphs for the elements scores, there does not
        appear to be any correlation.  None of the graphs
        rise and fall during the same intervals.  The missing element,
        satisfaction, is the most likely element to exhibit correlation,
        so the 4 elements analyzed here remain independent.

        To check the sensitivity of the CRI formula, the first method
        from Section \ref{sub:sensitivity} is used.  Small random
        values were added to the input values of the formulas. 
        Then the new values were used to calculated the element scores 
        at the respective Application ID or Project ID level.  Finally
        the new CRI element scores were compared with the previous
        scores from the unaltered data.  The goal is to show small
        changes in the input values result in small changes to the 
        CRI element score.  Figure \ref{fig:sensitivity} shows
        histograms of the new scores compared with the previous scores.
        None of the formulas exhibit too much sensitivity as the 
        histograms all indicate most of the score changes are small,
        as seen by the high peak of the histograms.

        \begin{figure}[ht]
            \centering
            \includegraphics[scale=.3]{images/sensitivity.png}
            \caption{CRI SENSITIVITY ANALYSIS}
            \label{fig:sensitivity}
        \end{figure}

        The random values added were based on the standard 
        deviations of the values in the column.
        Quality and Requirements used the standard deviation of the
        matching Application ID or Project ID.  This slight difference
        is due to the wide variation of standard deviations between
        Application IDs for Quality and Project IDs for Requirements. 
        Table \ref{tab:sensitivity} shows the columns that were
        altered for each element.

        \begin{longtable}{@{}l rr rrr}
            \toprule%
             \centering%
             {\bfseries CRI Element}
             & {\bfseries Columns Altered } \\

            \cmidrule[0.2pt](r{0.125em}){1-1}%
            \cmidrule[0.2pt](lr{0.125em}){2-2}%
            % \midrule
            \endhead

            Quality  & Development Effort, SIT Defects, UAT Defects \\
            \myrowcolour%
            Availability & Percent Uptime \\
            Schedule &  $\frac{\text{Schedule Finish - Actual Finish}}
                    {\text{Scheduled Finish - Scheduled Start}}$ \\
            \myrowcolour%
            Requirements & Actual Requirements Released \\

            \caption{CRI SENSITIVITY ANALYSIS}
            \label{tab:sensitivity}
        \end{longtable}

### 2015-03-06 paper_80_conclusion.tex
updated sensitivity analysis and conclusion added latest PDF file

There are many metrics that can be used to evaluate a Software Development Organization (SDO). 
Knowing which metrics to use and what they all mean can be a daunting task.  CRI is a
proposed solution to the difficulty of measuring an SDO.

Upon completion, this work shall identify:
\begin{itemize}
    \item Define \textbf{What} characteristics should be measured for an SDO
    \item Define \textbf{How} to measure those characteristics
    \item Map the relationship or lack of relationship with a Balanced Scorecard
    \item Create a Framework to store the necessary data for CRI
    \item Outline a Process to generate the CRI score
    \item Provide an example CRI score with real data
\end{itemize}

An entire software development organization (SDO) needs to be measured and analyzed properly, not just the development portion. This document has provided an overview of what indicators need to be measured for an SDO, and how those indicators can be combined to form a single number indicating the performance score of a software development organization.  Also, a framework to store this data was discussed.

>>>>

    There are many metrics that can be used to evaluate a Software
    Development Organization (SDO). The entire SDO needs to be measured 
    and analyzed properly, not just the development portion. 
    Knowing which metrics to use and what they all mean can be a daunting task.  
    This work identified the Cumulative Result Indicator (CRI) which is a
    proposed solution to the difficulty of measuring an SDO by creating a
    single number score for upper-level management to use to quickly gauge
    performance.

    The following have all been provided in this work.
    \begin{itemize}
        \item CRI defines what 5 elements of an SDO should be measured.
            Result indicators are included for quality, availability, satisfaction,
            schedule, and requirements. 
        \item CRI defines what data needs to be collected to create a 
            score for the 5 elements.
        \item CRI defines the formulas to create a score for the 5 elements.
        \item A process was outlined to generate the CRI score.
        \item An SDLC-AE was designed which includes a storage 
            framework for the necessary CRI data.
        \item A comparison with existing SDO evaluation techniques was presented.
        \item Finally, an example CRI score was calculated with data provided by
            an SDO organization within a large financial institution.
    \end{itemize}

    Now SDOs have a technique to consistently measure performance over time.  CRI
    should help upper-level management identify the areas of the organization
    that need attention and those that do not.  CRI should save time required to 
    evaluate the performance since the result is a single number.
